---
title: "ANCAT Analysis: 24-month-olds"
output:
  html_document:
    toc: true
    theme: united
---
  
Analysis Timestamp:

```{r}
date()
```

## Dependencies

```{r results='hide'}
library(ggplot2, quietly=T)
library(lme4, quietly=T)
library(psych, quietly=T)
library(dplyr, quietly=T)
```

## Raw data processing...

```{r results='hide', warning=FALSE}
source('./process_tobii_data_bf.R')
auto_process_tobii('ancat-aoi.txt','ancat-phasetiming.txt')
concat_csv('master.csv')

# fix subject names
master <- read.csv('master.csv')
master$ParticipantName <- gsub('[^a-zA-Z0-9]','',master$ParticipantName)
write.csv(master,'master.csv')

# prepare subjects file
subjects <- read.csv('subjects.csv')

prepare_master(subjectfile = './subjects.csv', trialfile = FALSE)

# create clean file
file.copy('master-prepared.csv','master-clean.csv',overwrite = T)

# exclude exclusions
master_clean <- read.csv('master-clean.csv')
master_clean <- master_clean[which(master_clean$Excluded == 0), ]

# get rid of additional Condition.x and use the Condition.y column from
# the subjects file
master_clean <- master_clean[ , -which(names(master_clean) %in% c("Condition.x"))]
names(master_clean)[names(master_clean)=="Condition.y"] <- "Condition"

# add KnownAnimal column
master_clean$KnownAnimal <- 0
master_clean[which(master_clean$Trial == 'UnfamiliarArmadillo' & master_clean$Armadillo == 1), 'KnownAnimal'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarFlamingo' & master_clean$Flamingo == 1), 'KnownAnimal'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarLizard' & master_clean$Lizard == 1), 'KnownAnimal'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarHedgehog' & master_clean$Hedgehog == 1), 'KnownAnimal'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarLemur' & master_clean$Lemur == 1), 'KnownAnimal'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarRhino' & master_clean$Rhinoceros == 1), 'KnownAnimal'] <- 1

# add KnownVerb column
master_clean$KnownVerb <- 0
master_clean[which(master_clean$Trial == 'UnfamiliarHedgehog' & master_clean$Condition == 'informative' & master_clean$Sleep == 1), 'KnownVerb'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarArmadillo' & master_clean$Condition == 'informative' & master_clean$Look == 1), 'KnownVerb'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarLizard' & master_clean$Condition == 'informative' & master_clean$Cry == 1), 'KnownVerb'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarFlamingo' & master_clean$Condition == 'informative' & master_clean$Dance == 1), 'KnownVerb'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarLemur' & master_clean$Condition == 'informative' & master_clean$Eat == 1), 'KnownVerb'] <- 1
master_clean[which(master_clean$Trial == 'UnfamiliarRhino' & master_clean$Condition == 'informative' & master_clean$Drink == 1), 'KnownVerb'] <- 1

# add Verb column
master_clean$Verb <- ''
master_clean[which(master_clean$Trial == 'UnfamiliarHedgehog'), 'Verb'] <- 'Sleep'
master_clean[which(master_clean$Trial == 'UnfamiliarArmadillo'), 'Verb'] <- 'Look'
master_clean[which(master_clean$Trial == 'UnfamiliarLizard'), 'Verb'] <- 'Cry'
master_clean[which(master_clean$Trial == 'UnfamiliarFlamingo'), 'Verb'] <- 'Dance'
master_clean[which(master_clean$Trial == 'UnfamiliarLemur'), 'Verb'] <- 'Eat'
master_clean[which(master_clean$Trial == 'UnfamiliarRhino'), 'Verb'] <- 'Drink'

# re-name factor levels.
levels(master_clean$Condition) <- c('Informative','Neutral')

# re-factor to get rid of any bad condition names which no longer exist in the dataset
# master_clean$Condition <- factor(as.character(trim(master_clean$Condition)))

#write.csv(master_clean,'master-clean.csv',row.names = FALSE)
save(master_clean,file='master-clean.Rdata')
```

## Load and set data options for **eyetrackingR** library.

```{r}
#devtools::install_github('jwdink/eyetrackingR')
library(eyetrackingR)

data <- make_eyetrackingr_data(master_clean, 
                       participant_column = "ParticipantName",
                       trial_column = "Trial",
                       time_column = "TimeFromPhaseOnset",
                       trackloss_column = "TrackLoss",
                       aoi_columns = c('Animate','Inanimate'),
                       treat_non_aoi_looks_as_missing = TRUE
)

# add kind of trial
data$TrialType <- ifelse(grepl('Unfamiliar',data$Trial), 'Unfamiliar','Familiar')
data$TrialType <- factor(data$TrialType)

# add Target for Familiar trials
data$Target <- as.factor( ifelse(test = grepl('(Spoon|Bottle)', data$Trial), 
                                       yes = 'Inanimate', 
                                       no  = 'Animate') )

# convert age
data$Age <- as.numeric(as.character(data$Age))
```

## Zoom in to response window

```{r}
response_window <- subset_by_window(data, window_start_time = 15500, window_end_time = 21000, rezero=TRUE, remove=TRUE)
```

# Familiar Trials

```{r}
familiar_raw <- filter(response_window, TrialType == 'Familiar')
```

## Clean by trackloss

```{r}
trackloss <- trackloss_analysis(data = familiar_raw)

# set a threshold for amount of trackloss that is acceptable
prop_thresh <- mean(trackloss$TracklossForTrial) + 2*sd(trackloss$TracklossForTrial)

familiar <- clean_by_trackloss(data = familiar_raw, trial_prop_thresh = prop_thresh)

trackloss_clean <- trackloss_analysis(data = familiar)
trackloss_clean_subjects <- unique(trackloss_clean[, c('ParticipantName','TracklossForParticipant')])

# get mean samples contributed per trials, with SD
mean(1 - trackloss_clean_subjects$TracklossForParticipant)
sd(1- trackloss_clean_subjects$TracklossForParticipant)

# get number of trials contributed by participant
interim_summary <- describe_data(familiar, 'Animate', c('ParticipantName'))
interim_summary

# remove participants who have less than 3 trials of either type
subjects_to_remove <- as.character(filter(interim_summary, NumTrials < 3)$ParticipantName)

familiar <- familiar %>%
                         filter(!(ParticipantName %in% subjects_to_remove))

# final counts:
final_summary <- describe_data(familiar, 'Animate', c('ParticipantName'))
final_summary

# how many participants?
length(unique(final_summary$ParticipantName))

# how many trials?
mean(final_summary$NumTrials)
sd(final_summary$NumTrials)
```

## Summarize 

```{r}
(familiar_summary <- familiar %>%
                    group_by(ParticipantName, Target) %>%
                    summarise(Animate = mean(Animate, na.rm=TRUE),
                              NTrials = length(unique(Trial))) %>%
                    ungroup() %>%
                    group_by(Target) %>%
                    summarise(MeanAnimate = mean(Animate),
                              SDAnimate = sd(Animate),
                              N = n(),
                              MeanTrials = mean(NTrials),
                              SDTrials = sd(NTrials)) %>%
                    ungroup())

subjects <- familiar %>%
            distinct(ParticipantName,Age_Group,Age,Sex,Condition) %>%
            group_by(Condition,Age_Group) %>%
            summarise(N=length(ParticipantName), MeanAge = mean(Age,na.rm=TRUE), N_Males = length(Sex[Sex=='M'])) %>%
            ungroup()

subjects
```

## Window Analysis

```{r}
familiar_summary <- describe_data(familiar, describe_column='Animate', group_columns=c('Target'))
familiar_summary

# agg by subject
familiar_sub <- make_time_window_data(familiar, 
                                       aois='Animate',
                                       predictor_columns=c('Target','Age','MCDI_Total'),
                                       summarize_by = "ParticipantName")

# take a quick peek at data
ggplot(familiar_sub, aes(x=Target,y=Prop,group=ParticipantName)) +
                      geom_point() +
                      geom_line()

# simple paired t-test between conditions
t.test(ArcSin ~ Target, data=familiar_sub, paired=TRUE)

# mixed-effects model
familiar_trial <- make_time_window_data(familiar, 
                                         aois='Animate', 
                                         predictor_columns=c('Target','Age'))

# sum-code and center predictors
familiar_trial$TargetC <- ifelse(familiar_trial$Target == 'Animate', .5, -.5)
familiar_trial$TargetC <- familiar_trial$TargetC - mean(familiar_trial$TargetC)

# mixed-effects linear model on subject*trial data
model <- lmer(ArcSin ~ TargetC + (1 | Trial) + (1 | ParticipantName), data = familiar_trial, REML = FALSE)
summary(model)
drop1(model,~.,test="Chi")
```

## Growth Curve Analysis

```{r}
# aggregate across trials within subjects in time analysis
response_time <- make_time_sequence_data(familiar, time_bin_size = 100, 
                                 predictor_columns = c("Target"),
                                 aois = "Animate"
                            )

# visualize time results
plot(response_time, predictor_column = "Target") + 
  theme_light() +
  coord_cartesian(ylim = c(0,1))

# sum-code and center our predictor:
response_time$TargetC <- ifelse(response_time$Target == 'Animate', .5, -.5)
response_time$TargetC <- response_time$TargetC - mean(response_time$TargetC)

# Construct model
model_time_sequence <- lmer(ArcSin ~ TargetC*(ot1+ot2+ot3+ot4) + (1 + ot1 + ot2 + ot3 + ot4 | Trial) + (1 + ot1 + ot2 + ot3 + ot4 | ParticipantName), data = response_time, REML = FALSE)
summary(model_time_sequence)

plot(response_time, predictor_column = "Target", dv = "ArcSin", model = model_time_sequence) + theme_light()
```

## Bootstrapped Spline Analysis

```{r}
response_familiar_time <- make_time_sequence_data(familiar,
                                  time_bin_size = 10, 
                                  predictor_columns = c("Target"),
                                  aois = "Animate",
                                  summarize_by = "ParticipantName"
                            )

# visualize timecourse
plot(response_familiar_time, predictor_column = "Target") + 
  theme_light() +
  coord_cartesian(ylim = c(0,1))

# bootstrap with smoothing splines
bootstrapped_familiar <- make_boot_splines_data(response_familiar_time, 
                                              predictor_column = 'Target', 
                                              within_subj = TRUE, 
                                              bs_samples = 5000, 
                                              alpha = .05,
                                              smoother = "smooth.spline")

plot(bootstrapped_familiar)

# show us the divergences where p < .05
bootstrap_analysis_familiar <- analyze_boot_splines(bootstrapped_familiar)
summary(bootstrap_analysis_familiar)
```

## Cluster Analysis

```{r}
alpha = .20
num_sub = length(unique((familiar$ParticipantName)))
threshold_t = qt(p = 1 - alpha/2, 
                 df = num_sub-1)

df_timeclust <- make_time_cluster_data(response_familiar_time, 
                                      test= "t.test",
                                      paired = TRUE,
                                      predictor_column = "Target", 
                                      threshold = threshold_t,
                                      formula = ArcSin ~ Target) 

plot(df_timeclust) +
  ylab("T-Statistic")

summary(df_timeclust)

clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=TRUE, paired=TRUE, samples=5000, parallel=TRUE)
clust_analysis

plot(clust_analysis)
```

## Onset-contingent Analysis

```{r}
# recode AOIs to target & distractor
familiar$TrialTarget <- ifelse(familiar$Target == 'Animate', familiar$Animate, familiar$Inanimate)
familiar$TrialDistractor <- ifelse(familiar$Target == 'Animate', familiar$Inanimate, familiar$Animate)

onsets <- make_onset_data(familiar, onset_time = 0, 
                          fixation_window_length = 100, target_aoi='TrialTarget')

# participants' ability to orient to the trial target overall:
plot(onsets) + theme(legend.text=element_text(size=5))

onset_switches <- make_switch_data(onsets, predictor_columns = c("Target","TrialNumber"))

# visualize subject's switch times
plot(onset_switches)

# center predictor:
onset_switches$FirstAOIC <- ifelse(onset_switches$FirstAOI == 'TrialTarget', .5, -.5)
onset_switches$FirstAOIC <- onset_switches$FirstAOIC - mean(onset_switches$FirstAOIC, na.rm=TRUE)
onset_switches$TargetC <- ifelse(onset_switches$Target == 'Animate', .5, -.5)
onset_switches$TargetC <- onset_switches$TargetC - mean(onset_switches$TargetC)
onset_switches$TrialNumberC <- onset_switches$TrialNumber - mean(onset_switches$TrialNumber)

# build model:
model_switches <- lmer(FirstSwitch ~ (FirstAOIC+TargetC+TrialNumberC)^2 + (1 | Trial) + (1 + TargetC | ParticipantName), data=onset_switches, REML=FALSE)
summary(model_switches)
drop1(model_switches,~.,test="Chi")
```

# Unfamiliar Trials

```{r}
unfamiliar_raw <- filter(response_window, TrialType == 'Unfamiliar')
```

## Clean by trackloss

```{r}
trackloss <- trackloss_analysis(data = unfamiliar_raw)

# set a threshold for amount of trackloss that is acceptable
prop_thresh <- mean(trackloss$TracklossForTrial) + 2*sd(trackloss$TracklossForTrial)

unfamiliar <- clean_by_trackloss(data = unfamiliar_raw, trial_prop_thresh = prop_thresh)

trackloss_clean <- trackloss_analysis(data = unfamiliar)
trackloss_clean_subjects <- unique(trackloss_clean[, c('ParticipantName','TracklossForParticipant')])

# get mean samples contributed per trials, with SD
mean(1 - trackloss_clean_subjects$TracklossForParticipant)
sd(1- trackloss_clean_subjects$TracklossForParticipant)

# get number of trials contributed by participant
interim_summary <- describe_data(unfamiliar, 'Animate', c('ParticipantName'))
interim_summary

# remove participants who have less than 3 trials of either type
subjects_to_remove <- as.character(filter(interim_summary, NumTrials < 3)$ParticipantName)

unfamiliar <- unfamiliar %>%
                         filter(!(ParticipantName %in% subjects_to_remove))

# final counts:
final_summary <- describe_data(unfamiliar, 'Animate', c('ParticipantName'))
final_summary

# how many participants?
length(unique(final_summary$ParticipantName))

# how many trials?
mean(final_summary$NumTrials)
sd(final_summary$NumTrials)
```

## Summarize 

```{r}
(unfamiliar_summary <- unfamiliar %>%
                    group_by(ParticipantName, Target) %>%
                    summarise(Animate = mean(Animate, na.rm=TRUE),
                              NTrials = length(unique(Trial))) %>%
                    ungroup() %>%
                    group_by(Target) %>%
                    summarise(MeanAnimate = mean(Animate),
                              SDAnimate = sd(Animate),
                              N = n(),
                              MeanTrials = mean(NTrials),
                              SDTrials = sd(NTrials)) %>%
                    ungroup())

subjects <- unfamiliar %>%
            distinct(ParticipantName,Age_Group,Age,Sex,Condition) %>%
            group_by(Condition,Age_Group) %>%
            summarise(N=length(ParticipantName), MeanAge = mean(Age,na.rm=TRUE), N_Males = length(Sex[Sex=='M'])) %>%
            ungroup()

subjects
```

## Window Analysis

```{r}
unfamiliar_summary <- describe_data(unfamiliar, describe_column='Animate', group_columns=c('Condition'))
unfamiliar_summary

# agg by subject
unfamiliar_sub <- make_time_window_data(unfamiliar, 
                                       aois='Animate',
                                       predictor_columns=c('Condition','Age','MCDI_Total'),
                                       summarize_by = "ParticipantName")

# take a quick peek at data
ggplot(unfamiliar_sub, aes(x=Condition,y=Prop)) +
                      geom_boxplot() +
                      geom_point()

# simple paired t-test between conditions
t.test(ArcSin ~ Condition, data=unfamiliar_sub, var.equal=T)

# mixed-effects model
unfamiliar_trial <- make_time_window_data(unfamiliar, 
                                         aois='Animate', 
                                         predictor_columns=c('Condition','Age'))

# sum-code and center predictors
unfamiliar_trial$ConditionC <- ifelse(unfamiliar_trial$Condition == 'Informative', .5, -.5)
unfamiliar_trial$ConditionC <- unfamiliar_trial$ConditionC - mean(unfamiliar_trial$ConditionC)

unfamiliar_trial$AgeC <- unfamiliar_trial$Age - mean(unfamiliar_trial$Age,na.rm=T)

# mixed-effects linear model on subject*trial data
model <- lmer(ArcSin ~ ConditionC + (1 | Trial) + (1 | ParticipantName), data = unfamiliar_trial, REML = FALSE)
summary(model)
drop1(model,~.,test="Chi")
```

## Growth Curve Analysis

```{r}
# aggregate across trials within subjects in time analysis
response_time <- make_time_sequence_data(unfamiliar, time_bin_size = 100, 
                                 predictor_columns = c("Condition","Age_Group"),
                                 aois = "Animate"
                            )

# visualize time results
plot(response_time, predictor_column = "Condition") + 
  theme_light() +
  coord_cartesian(ylim = c(0,1))

response_time_sub <- response_time %>%
                     group_by(ParticipantName,Condition,Age_Group,Time) %>%
                     summarise(Prop=mean(Prop,na.rm=TRUE)) %>%
                     ungroup()

ggplot(response_time_sub, aes(x=Time, y=Prop, color=Condition, fill=Condition)) +
              stat_summary(fun.y='mean', geom='line') +
              stat_summary(fun.data='mean_cl_normal', geom='ribbon', alpha=.3, color=NA, fun.args=list(mult=1)) +
              facet_grid(~Age_Group)

# sum-code and center our predictor:
response_time$ConditionC <- ifelse(response_time$Condition == 'Informative', .5, -.5)
response_time$ConditionC <- response_time$ConditionC - mean(response_time$ConditionC)

# Construct model
model_time_sequence <- lmer(ArcSin ~ ConditionC*(ot1+ot2+ot3+ot4) + (1 + ot1 + ot2 + ot3 + ot4 | Trial) + (1 + ot1 + ot2 + ot3 + ot4 | ParticipantName), data = response_time, REML = FALSE)
summary(model_time_sequence)

plot(response_time, predictor_column = "Condition", dv = "ArcSin", model = model_time_sequence) + theme_light()
```

## Bootstrapped Spline Analysis

```{r}
response_unfamiliar_time <- make_time_sequence_data(unfamiliar,
                                  time_bin_size = 10, 
                                  predictor_columns = c("Condition","Age_Group"),
                                  aois = "Animate",
                                  summarize_by = "ParticipantName"
                            )

# visualize timecourse
plot(response_unfamiliar_time, predictor_column = "Condition") + 
  theme_light() +
  coord_cartesian(ylim = c(0,1))

# get rid of NA's so we can use splines
response_unfamiliar_time_nonas <- response_unfamiliar_time[!is.na(response_unfamiliar_time$Prop), ]

# bootstrap with smoothing splines
bootstrapped_unfamiliar <- make_boot_splines_data(response_unfamiliar_time_nonas, 
                                              predictor_column = 'Condition', 
                                              within_subj = FALSE, 
                                              bs_samples = 5000, 
                                              alpha = .05,
                                              smoother = "smooth.spline")

plot(bootstrapped_unfamiliar)

# show us the divergences where p < .05
bootstrap_analysis_unfamiliar <- analyze_boot_splines(bootstrapped_unfamiliar)
summary(bootstrap_analysis_unfamiliar)
```

## Cluster Analysis

```{r}
alpha = .20
num_sub = length(unique((response_unfamiliar_time$ParticipantName)))
threshold_t = qt(p = 1 - alpha/2, 
                 df = num_sub-1)

# differences in positive direction...
df_timeclust <- make_time_cluster_data(response_unfamiliar_time, 
                                      test= "t.test",
                                      paired = FALSE,
                                      predictor_column = "Condition", 
                                      threshold = threshold_t,
                                      formula = ArcSin ~ Condition) 

plot(df_timeclust) +
  ylab("T-Statistic")

summary(df_timeclust)

clust_analysis <- analyze_time_clusters(df_timeclust, within_subj=FALSE, paired=FALSE, samples=5000, parallel=TRUE)
clust_analysis

plot(clust_analysis)
```

## Onset-contingent Analysis

```{r}
onsets <- make_onset_data(unfamiliar, onset_time = 0, 
                          fixation_window_length = 100, target_aoi='Animate')

# participants' ability to orient to the trial target overall:
plot(onsets, predictor_columns = "Condition") + theme(legend.text=element_text(size=5))

onset_switches <- make_switch_data(onsets, predictor_columns = c("Condition","TrialNumber"))

# visualize subject's switch times
plot(onset_switches, predictor_columns = "Condition")

# center predictor:
onset_switches$FirstAOIC <- ifelse(onset_switches$FirstAOI == 'Animate', .5, -.5)
onset_switches$FirstAOIC <- onset_switches$FirstAOIC - mean(onset_switches$FirstAOIC, na.rm=TRUE)
onset_switches$ConditionC <- ifelse(onset_switches$Condition == 'Informative', .5, -.5)
onset_switches$ConditionC <- onset_switches$ConditionC - mean(onset_switches$ConditionC)
onset_switches$TrialNumberC <- onset_switches$TrialNumber - mean(onset_switches$TrialNumber)

# build model:
model_switches <- lmer(FirstSwitch ~ (FirstAOIC+ConditionC+TrialNumberC)^2 + (1 | Trial) + (1 | ParticipantName), data=onset_switches, REML=FALSE)
summary(model_switches)
drop1(model_switches,~.,test="Chi")

# within Informative, to look for speed-up over trials:
model_switches_inf <- lmer(FirstSwitch ~ (FirstAOIC+TrialNumberC)^2 + (1 | Trial) + (1 | ParticipantName), data=onset_switches %>% filter(Condition == 'Informative'), REML=FALSE)
summary(model_switches_inf)
drop1(model_switches_inf,~.,test="Chi")

(onset_switches %>%
    filter(Condition == 'Informative') %>%
    mutate(Half = ifelse(TrialNumber <= 9, 'First', 'Last')) %>%
    group_by(ParticipantName,Half,FirstAOI) %>%
    summarise(
      FirstSwitch = mean(FirstSwitch,na.rm=T)
    ) %>%
    group_by(Half,FirstAOI) %>%
    summarise(
      M = mean(FirstSwitch,na.rm=T),
      SD = sd(FirstSwitch,na.rm=T)
    ))
```

# Dump Data for Individual Differences

```{r}
familiar_divergence <- subset_by_window(familiar, window_start_time = 170, window_end_time = 5330, rezero=TRUE, remove=TRUE)

familiar_divergence_agg <- make_time_window_data(familiar_divergence, 
                                       aois='Animate',
                                       predictor_columns=c('Target','Age','MCDI_Total','MCDI_Nouns','MCDI_Verbs'),
                                       summarize_by = "ParticipantName")

unfamiliar_divergence <- subset_by_window(unfamiliar, window_start_time = 900, window_end_time = 1930, rezero=TRUE, remove=TRUE)

unfamiliar_divergence_agg <- make_time_window_data(unfamiliar_divergence, 
                                       aois='Animate',
                                       predictor_columns=c('Condition','Age','MCDI_Total','MCDI_Nouns','MCDI_Verbs'),
                                       summarize_by = "ParticipantName")

write.csv(familiar_divergence_agg,'familiar_divergence_agg_24.csv')
write.csv(unfamiliar_divergence_agg,'unfamiliar_divergence_agg_24.csv')
```



